An Analysis of the Use of Average Centipawn Loss to Detect Cheating in Chess

### 2022-11-14 Manuscript/manuscript.tex
added some figures

%% preamble
\usepackage[margin = 1in]{geometry}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% metadata
\title{An Analysis of the Use of Centipawn Loss to Detect Cheating in Chess}
\author{James Horbury\\
    University of Connecticut
}
\date{November 14, 2022}

@@

@@

>>>>

%% preamble
\usepackage[margin = 1in]{geometry}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{graphicx}

%% metadata
\title{An Analysis of the Use of Average Centipawn Loss to Detect Cheating in Chess}
\author{James Horbury\\
    University of Connecticut
}
\date{November 14, 2022}

@@

% how to make individual images that are different resolutions the same size?

\includegraphics[scale=0.3]{niemann_rating.png}

\includegraphics[scale=0.5]{carlsen_rating.png}

% report statistical analysis in tables/figures, summarize what they mean
% discussion to link analysis back to topic

@@

% summarize contributions of research and future directions
The results of this research largely confirm the claims included in Chess.com's report on Niemann however, although the data does indicate suspicious activity, this is not a "cut and dry" case of cheating, so to speak. Observing a single method to detect cheating as we have through average centipawn loss is not enough to confirm for sure that Hans Niemann cheated, both virtually and OTB, more than he claimed but this was never truely the objective of this research. The real question posed here was whether historical records of average centipawn loss compared to his ELO ranking could be treated as a "smoking gun" or surefire way to prove cheating alone; which it does not. Note: Relevant figures not available, fix this later.
